# Title & Subtitle Issues {#title-issues}

```{r include=FALSE}
library(ArabBarometR)
```

Title and subtitle issues often go hand-in-hand, and the process for solving them is often the same, so both will be addressed here. As shorthand, the guide will use "title" in place of "title and subtitle" unless otherwise explicitly stated.

-   [Title is not showing up](#no-title)
-   [Title is wrong](#wrong-title)
-   [Title does not fit on graph](#title-too-large)
-   [Title does not display correctly due to language issues](##title-render-issue)
-   [Only title or only subtitle is showing up](##title-OR-subtitle)

## Title/subtitle is not showing up {#no-title}

There are a few reasons a graph's title may not appear. In order from most to least likely, it could be:

-   [the question number for the summary is wrong](#wrong-numb-user);
-   [the question number in the titles reference sheet is wrong](#wrong-num-titlesheet);
-   [the question number does not have a title in the titles reference sheet](#wrong-num-titlesheet);
-   [the function does not automatically supply a title for the graph](#no-auto-title); or
-   [the default has been changes from `.title = TRUE` to `.title = FALSE`](#default-change).

### Wrong Question Number, User Error {#wrong-numb-user}

The first step is to check if you are summarizing the correct question. You may automatically think, *``Of course I'm summarizing the correct question! I'm the one who's deciding which question to summarize! I'm going to skip this section!''* 

Please don't.

This is most often the case when trying to create a comparative plot for the first category of a nominal question. For example, say you want to the percent of the population who said the economic situation was the most pressing issue facing their country across countries. You might type the following:

```{r no-title-1,error=TRUE, fig.dim=c(13,12)}

# English
calculate_smry_comp(abwave7_eng,
                    "Q2061A") %>%
  plot_smry_comp(.caption = "Arab Barometer Wave VII (2021-2022)")

# Arabic
calculate_smry_comp(abwave7_ara,
                    "Q2061A") %>%
  plot_smry_comp(.caption = "Arab Barometer Wave VII (2021-2022)")

```

You get a graph and the numbers are correct. What gives?

What gives is that `Q2061A` is a **nominal question**. The summary functions in the `ArabBarometR` package only summarize the response values of `1` for nominal questions. You see the correct values because you are comparing the first category.

How do you know the type of question you are trying to plot? One rule of thumb is that if the question is not on a scale and has multiple different choices, it's probably nominal. Another way to tell is to use the handy `type_test()` function provided by the `ArabBarometR` package. The only input is a character string of the variable. The function outputs the type that variable is classified as.

```{r no-title-2}

type_test("Q2061A")

```

Ok, so then why don't you see a title? You don't see a title because this is a nominal question *and* a comparative graph. The titles sheet that `ArabBarometR` uses to call titles for **comparative** plots expects all nominal questions to be dummied out. That is, if variable `Q999` is a nominal question with `N` categories, there is a comparative title for `Q999_1`, `Q999_2`, ... , `Q999_N`. There is NOT a comparative title for `Q999`.

**How to Fix It** Now that you know why the title isn't showing up, you probably have a good idea of how to fix it.

1.  Make sure your nominal variable is dummied out.
2.  Re-do your code with the correct variable name.

The `ArabBarometR` package provides two useful methods for creating dummies: `dummy_all()` and `dummy_select()`. The `dummy_all()` function will create a dummy variable for every level of the original variable. The `dummy_select()` function will create a dummy variable for a specific level of the original variable. That is, `dummy_all(abwave7,Q999)` and `dummy_select(abwave7,Q999,.dmy_lvl = 1)` will both create the variable `Q999_1`, but only `dummy_all()` will create `Q999_2` through `Q999_N`.

Below we can see what happens when we correct our code.

```{r no-title-3, fig.dim=c(13,12)}

# English
abwave7_eng <- dummy_all(abwave7_eng,Q2061A)

calculate_smry_comp(abwave7_eng,
                    "Q2061A_1") %>%
  plot_smry_comp(.caption = "Arab Barometer Wave VII (2021-2022)")

# Arabic
abwave7_ara <- dummy_all(abwave7_ara,Q2061A)

calculate_smry_comp(abwave7_ara,
                    "Q2061A_1") %>%
  plot_smry_comp(.caption = "Arab Barometer Wave VII (2021-2022)")
```

Fixed!

### Wrong Question Number, Titles Sheet Errors I & II {#wrong-num-titlesheet}

Ok, so what if you're not trying to create a comparative plot for a nominal question and there's still no title? Then it's time to look at whether there is an issue with the titles sheet. It could be that (1) the question number in the reference sheet is incorrect or (2) there is no title associated with that question number.

The first step is to verify that there is no title associated with the question number you are trying to graph, regardless of *why* there is no title. This can be done using the `title_function()` and `subtitle_function()` from the `ArabBarometR` package. These functions are primarily used internally in the `plot_` functions to call up titles and subtitles, but they can also be used on the front-end to verify titles.

These functions take four inputs:

1. `.title`/`.subtitle` : A title the user wants to use OR a logical value indicating whether a title should be returned automatically; i.e., the title/subtitle is expected to be in the titles sheet.
2. `.var` : The question number as a character string; e.g., `"Q999"`.
3. `.language` : Either `"English"` or `"Arabic"` depending on the language of the graph.
4. `.graph_type` : Either `"individual"` or `"comparative"` depending on the type of graph you want to make.

You can use these functions to see why no title was provided in the example for section \@ref(wrong-numb-user). Before the corrections were made, the `plot_smry_comp()` function was doing the following internally:

```{r no-title-4}

# English
title_function(TRUE,             # Automatically supply the title
               "Q2061A",         # Look for the title for variable Q2061A
               "English",        # Provide the English title
               "comparative")    # For a comparative graph

subtitle_function(TRUE,             # Automatically supply the subtitle
                  "Q2061A",         # Look for the subtitle for variable Q2061A
                  "English",        # Provide the English subtitle
                  "comparative")    # For a comparative graph


# Arabic
title_function(TRUE,             # Automatically supply the title
               "Q2061A",         # Look for the title for variable Q2061A
               "Arabic",         # Provide the Arabic title
               "comparative")    # For a comparative graph

subtitle_function(TRUE,             # Automatically supply the subtitle
                  "Q2061A",         # Look for the subtitle for variable Q2061A
                  "Arabic",         # Provide the Arabic subtitle
                  "comparative")    # For a comparative graph

```

The functions return no value because there is no `Q2061A` in the comparative titles sheet. Once the question number was corrected, the `plot_smry_comp()` was instead doing the following internally:

```{r no-title-5}

# English
title_function(TRUE,             # Automatically supply the title
               "Q2061A_1",       # Look for the title for variable Q2061A
               "English",        # Provide the English title
               "comparative")    # For a comparative graph

subtitle_function(TRUE,             # Automatically supply the subtitle
                  "Q2061A_1",       # Look for the subtitle for variable Q2061A
                  "English",        # Provide the English subtitle
                  "comparative")    # For a comparative graph


# Arabic
title_function(TRUE,             # Automatically supply the title
               "Q2061A_1",       # Look for the title for variable Q2061A
               "Arabic",         # Provide the Arabic title
               "comparative")    # For a comparative graph

subtitle_function(TRUE,             # Automatically supply the subtitle
                  "Q2061A_1",       # Look for the subtitle for variable Q2061A
                  "Arabic",         # Provide the Arabic subtitle
                  "comparative")    # For a comparative graph

```

If you use the functions and don't get a value, that variable (spelled as-is) does not have a title. This could be for the reason listed above: (1) the variable is incorrectly named in the reference sheet, or (2) the variable is not in the reference sheet.

**How to Fix It**

*Short Term*: For a graph you need immediately, you can supply your own title and subtitle. In every `plot_` function, there is a `.title` and `.subtitle` parameter that can be used just like the `.caption` parameter. That is, the user supplies a string for each parameter and those strings become the title and subtitle.

*Long Term*: For a permanent fix, first identify if the title is missing/misspelled from the `ArabBarometR` package, the latest Google Drive titles sheet, or both.

In the package, there are four title data frames: `titles_comparative_ar`, `titles_single_country_ar`, `titles_comparative_en`, and `titles_single_country_en`. These data frames contain all the Arabic comparative titles, Arabic single country titles, English comparative titles, and English single country titles, respectively. You can use `View(dataframe)` to look at the data frames.

Currently, the location of the titles sheet on Google Drive will likely depend on the Wave.^[Hopefully in the future there will be one master titles sheet we add to each Wave as necessary.]

The package draws the titles from the sheet on Google Drive. Let the team know you are making updates to the titles sheet on the Google Drive, for which question, why, and when you are finished with the corrections. Once the corrections are done, MC will update the package.

### No Automatic Title/Subtitle {#no-auto-title}

There are a few functions which do not automatically supply a title. This is common for functions that plot multiple question, as the package cannot anticipate every combination of questions that could be plotted together. This will also happen if you create your own variable to graph. In these cases, the onus is on the user to supply a title.

For example, say you wanted to make a comparative graph showing the percent of citizens who say the current economic situation in their country is bad or very bad (`Q101`, response values 3 and 4). The default settings for this question would produce the opposite: the percent of citizens who say the current economic situation in their country is good or very good. The most straightforward way to create this graph is to create a new variable and plot that.

```{r no-title-6, fig.dim=c(13,12)}

abwave7_eng$bad_economy <- ifelse(abwave7_eng$Q101 %in% 3:4, 1, 0)

calculate_smry_comp(abwave7_eng,
                    "bad_economy",
                    .type = "dichotomous") %>%
  plot_smry_comp(.caption = "Arab Barometer Wave VII (2021-2022)")

```

Essentially, inside the `plot_smry_comp()` function, the functions `title_function()` and `subtitle_function()` are once again returning nothing, since the variable "bad_economy" is not in the title data frames.

**How to Fix It** In this case, you must supply your own title. This is a feature that will remain constant. It is unreasonable to expect the package to predict exactly what kind of custom graphs you will produce. Just remember to include a title!

```{r no-title-7}

abwave7_eng$bad_economy <- ifelse(abwave7_eng$Q101 %in% 3:4, 1, 0)

calculate_smry_comp(abwave7_eng,
                    "bad_economy",
                    .type = "dichotomous") %>%
  plot_smry_comp(.title = "How is the economy doing in your country?",
                 .subtitle = "% saying bad or very bad",
                 .caption = "Arab Barometer Wave VII (2021-2022)")

```

### Default Change {#default-change}

Finally, it could be that the default setting for supplying a title has changed. By default, every `plot_` function for which a title can be automatically supplied^[See section \@ref(no-auto-title) for why not every function can supply a title.], does automatically supply a title.

Although it is extremely unlikely, it could be that the `ArabBarometR` default changed so `plot_` functions no longer supply a title. If this is the case, a warning has certainly gone out that this change is coming/has come and a note has been made in the record of `ArabBarometR` versioning. To check the default setting of a function, view that function's help page. You can do this by typing `?function_name()` in your R console. On the help page, look for what the `.title` parameter is set to. If you see `.title = F` or `.title = FALSE`, the default has changed so the function no longer automatically supplies the title.

```{r no-title-8}

?plot_smry_comp

```

It could also be that perhaps you turned off the default to check something else when debugging and forgot to switch it back. In this case, you would have explicitly set the `.title` parameter to `FALSE`.


```{r no-title-9, fig.dim=c(13,12)}

# English
calculate_smry_comp(abwave7_eng,
                    "Q2061A_1") %>%
  plot_smry_comp(.title = FALSE,
                 .subtitle = F,
                 .caption = "Arab Barometer Wave VII (2021-2022)")

```

**How to Fix It** Set the `.title` and/or `.subtitle` parameter to `TRUE` or `T`.


```{r no-title-10, fig.dim=c(13,12)}

# English
calculate_smry_comp(abwave7_eng,
                    "Q2061A_1") %>%
  plot_smry_comp(.title = FALSE,
                 .subtitle = T,
                 .caption = "Arab Barometer Wave VII (2021-2022)")

```

## Title/Subtitle is Wrong {#wrong-title}

There are three ways the title and subtitle may appear incorrect on the graph.

* [User supplied incorrect title](#wrong-title-user)
* [Wrong title in title sheets](#wrong-title-package)
* Title in wrong language

### Wrong Title, User Error {#wrong-title-user}

The first place to begin figuring out errors is always your own code. Misspellings are exceedingly common when we're trying to get many things done at once.

For example, say you want to emphasize that we asked what people thought was the most important challenge facing not just any country, but *their* country, so you want to change the title of a graph for Q2061A from "Most important challenge facing **the** country" to "Most important challenge facing **your** country". Say you use the following code.

```{r wrong-title-1, fig.dim=c(13,12)}

calculate_smry_comp(abwave7_eng,
                    "Q2061A_1") %>%
  plot_smry_comp(.title = "Most important challeng facing your country",
                 .caption = "Arab Barometer Wave VII (2021-2022)")

```

What's wrong?

Good catch- "challenge" is spelled wrong.

**How to Fix It** Simply correct your spelling.

```{r wrong-title-2, fig.dim=c(13,12)}

calculate_smry_comp(abwave7_eng,
                    "Q2061A_1") %>%
  plot_smry_comp(.title = "Most important challenge facing your country",
                 .caption = "Arab Barometer Wave VII (2021-2022)")

```

### Wrong Title, Package Error {#wrong-title-package}

If you are using the default title for the question and it appears incorrectly, there is likely an issue with the titles sheet. You can be sure of this using the `title_function()` and `subtitle_function()` discussed in section \@ref(wrong-num-titlesheet). The text supplied by these functions is the default title and subtitle for the graphs.

**How to Fix It** Follow the same steps described in section \@ref(wrong-num-titlesheet).

## Title/subtitle Does Not Fit {#title-too-large}

If for whatever reason you are creating a graph with an extremely long title using many words, the title may run off the graph. Most plotting functions wrap titles by default, but some do not^[Eventually, they all will.].

```{r long-title-1, fig.dim=c(13,12)}

plot_multiquestions_comp(abwave7_eng,
                        c("Q101",
                          "Q102"),
                        c("Current economic system",
                          "Future economic system"),
                        .title = "An extremely long title with lots and lots and lots and lots and lots and lots and lots and lots of words.",
                        .subtitle = "% of people who say they absolutely, unequivicably want an even longer subtitle",
                        .caption = "Arab Barometer Wave VII (2021-2022)",
                        .language = "en")

calculate_smry_comp(abwave7_eng,
                    "Q2061A_1") %>%
  plot_smry_comp(.title = ,
                 .caption = "Arab Barometer Wave VII (2021-2022)")

```

## Title/subtitle Displays Incorrectly - Language {#title-render-issue}

## Only Title OR Subtitle Showing Up {#title-OR-subtitle}